Energy and the CES production function

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Added second alpha option. Cleaning sigma graph.

<<model_points>>=
model_points_style <- function(p) {
  p + 
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
  scale_shape_manual(values = c(21, 21, 23:27)) +
  guides( 
    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
}

@

@@

@@

<<fig.width=8.5, fig.height=5, out.width=".9\\textwidth">>=
p <- 
ggplot(
  AllCoeffs %>% 
    gather(type, value, matches("sigma")) %>% 
    filter(!is.na(value)) %>% 
    filter(! type %in% c("sigma", "sigma_1")) %>%
    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor) 
  ) + 
  geom_point(aes(x=.0001 + value, y=type, 
                 shape = Model, fill=Model, size=Model,
                 color=Inputs
                 )
                 #position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( type ~ Country, scales = "free_y" ) + 
  scale_x_log10(limits = c(0.001,2000)) +
  xy_theme() +
  theme(legend.position="top")

@@

<<sigma_graph>>=
### A function named blah_function should return a function, not a plot.  Don't use function in the name 
### of a function unless it tells you something about the function.  All functions are functions, we don't
### need to name them like that.

@@

<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
@

<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
@

@@

myXTable(data_CSP_CD,
         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

<<fig.height=3>>=

p <- triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model,
      color = Inputs)
  ) +
  facet_grid(. ~ Country)
  model_points_style(p)
@

Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
and the reference model (exponential-only).
%
<<CD_coeffs, results="asis">>=
data_CD_exp <- 
  AllCoeffs %>% 
  filter(model=="CD" | model=="exp") %>% 
  select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse)

>>>>

<<model_points>>=
model_points_style <- function(p) {
  p + 
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
  scale_shape_manual(values = c(21, 21, 23:27)) +
  guides( 
    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
}
@

@@

<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=7.5, fig.height=2.8, fig.cap="Ternary graph of output elasticities~($\\alpha$). This version shows all Unadjusted and Quality-adjusted points on the same graph. Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
p <- triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model,
      color = Inputs)
  ) +
  facet_grid(. ~ Country)
  model_points_style(p)
@

<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=7.5, fig.height=5, fig.cap="Ternary graph of output elasticities~($\\alpha$). This version splits the Unadjusted and Quality-adjusted values on their own graphs. This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model
      # color = Inputs
      )
  ) +
  facet_grid(Inputs ~ Country) +

    # model_points_style(p)

  # scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
  scale_shape_manual(values = c(21, 21, 23:27)) +
  guides( 
    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
@

@@

<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$).">>=
p <- 
ggplot(
  AllCoeffs %>% 
    gather(type, value, matches("sigma")) %>% 
    filter(!is.na(value)) %>% 
    filter(! type %in% c("sigma", "sigma_1")) %>%
    mutate(Model = interaction(nest, CSP, sep = " ", drop=TRUE),
           Inputs = flavor
           )
  ) + 
  geom_point(aes(x=value, y=type, 
                 shape = Model, fill=Model, size=Model,
                 color=Inputs
                 )
                 #position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( type ~ Country, scales = "free_y" ) + 
  scale_x_log10(limits = c(0.001,2000)) +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  xy_theme() +
  theme(legend.position="top")

@@

<<sigma_graph, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
### A function named blah_function should return a function, not a plot.  Don't use function in the name 
### of a function unless it tells you something about the function.  All functions are functions, we don't
### need to name them like that.

@@

<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.", eval=FALSE, include=FALSE>>=
sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
@

<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
@

@@

myXTable(data_CSP_CD,
         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
and the reference model (exponential-only).
%
<<CD_coeffs, results="asis">>=
data_CD_exp <- 
  AllCoeffs %>% 
  filter(model=="CD" | model=="exp") %>% 
  select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse)
